Goal is to show that

The functor category with values in $\kmat$ is an Abelian category with enough projectives (constructively) and direct sum decomposition (constructively).

\subsection{Abelian category}

\begin{lemma}
Let $\mathcal{A}$ be a finite-dimensional algebroid over some field $\Bbbk$. The functor category
\[
\HomAkmat
\]
is an Ab-category.
\begin{proof}
\begin{itemize}
\renewcommand{\labelenumi}{(\theenumi)}
\item Let $F, G \in \mathrm{Hom}(\mathcal{A},\kmat)$. We want to show that
$\mathrm{Hom}_{\mathrm{Hom}(\mathcal{A},\kmat)}(F,G)$ is an abelian group.
We define the morphisms in $\mathrm{Hom}(\mathcal{A},\kmat)_{1}$ as natural transformations
between the functors, i.e. a morphism $\eta F \Rightarrow G$ is defined by its components $\eta_{o}$ for each object $o \in \mathcal{A}$,
such that $G(o) = \eta_{o} F(o)$. Each $\eta_{o}$ is a morphism in $\kmat$, i.e. a matrix. And for these we already
showed that it's an abelian category, therefore $\mathrm{Hom}_{\mathrm{Hom}(\mathcal{A},\kmat)}(F,G)$ is an abelian group.
\item The composition of two morphisms $\eta, \gamma \in \mathrm{Hom}(\mathcal{A},\kmat)_{1}$ 
\end{itemize}
\end{proof}
\end{lemma}

\begin{theorem}\label{thm:functor_category_abelian}
Let $\mathcal{A}$ be a finite-dimensional algebroid over some field $\Bbbk$. The functor category $\HomAkmat$
is an abelian category.
\end{theorem}
\begin{proof}
We prove that $\HomAkmat$ is an Ab-category, then that it is also an additive category and a pre-abelian category and finally that
it is an abelian category.
\begin{enumerate}
\renewcommand{\labelenumi}{(\theenumi)}
\item In order to show that $\HomAkmat$ is an Ab-category, we must show that 
\begin{enumerate}
\renewcommand{\labelenumii}{(\roman{enumii})}
\item for any two objects $F,G \in \HomAkmat_{0}$ the hom-set $\mathrm{Hom}_{\HomAkmat}(F,G)$ between them is an Abelian group, and
\item that the composition of two morphisms\\
$\mu : \mathrm{Hom}_{\HomAkmat}(F,G) \times \mathrm{Hom}_{\HomAkmat}(G,H) \rightarrow \mathrm{Hom}_{\HomAkmat}(F,H)$ is a
bilinear map, i.e. for $\eta, \varepsilon \in \mathrm{Hom}_{\HomAkmat}(F,G)$ and $\varphi, \psi \in \mathrm{Hom}_{\HomAkmat}(G,H)$ and
for $x \in \Bbbk$
\begin{align}
(\eta + \varepsilon)\varphi &= \eta\varphi + \varepsilon\varphi \\
\eta(\varphi + \psi) &= \eta\varphi + \eta\psi \\
(x\eta)\varphi &= \eta(x\varphi) = x(\eta\varphi).
\end{align}
\end{enumerate}

\begin{subproof}[Proof of (i)]
For any object $c \in \mathcal{A}$, the set of components $\mathrm{Hom}_{\kmat}(Fc,Gc)$ is a $\Bbbk$-vector space and therefore an
Abelian group.

We define the addition and scalar multiplication
\begin{align*}
+ :&& \mathrm{Hom}_{\HomAkmat}(F,G) &\times \mathrm{Hom}_{\HomAkmat}(F,G) \rightarrow \mathrm{Hom}_{\HomAkmat}(F,G)\\
\cdot :&& \Bbbk &\times \mathrm{Hom}_{\HomAkmat}(F,G) \rightarrow \mathrm{Hom}_{\HomAkmat}(F,G)
\end{align*}
component-wise: $\forall \eta, \varepsilon \in \mathrm{Hom}_{\HomAkmat}(F,G), \forall x \in \Bbbk, \forall c \in \mathcal{A}$
\begin{align}
(\eta+\varepsilon)_{c} &:= \eta_{c} + \varepsilon_{c}\\
(x \eta)_{c} &:= x\eta_{c}
\end{align}
where the right-hand side is the usual addition and scalar multiplication of matrices.

We identify as the neutral element $0_{F,G} \in \mathrm{Hom}_{\HomAkmat}(F,G)$ (or simply $0$ when the context is clear)
the natural transformation $0$ with each component $0_{c}$ being the $Fc\times Gc$ zero matrix.
For each natural transformation $\eta$ the additive inverse $-\eta$ is defined component-wise as
\begin{align}
(-\eta)_{c} &:= -\eta_{c}.
\end{align}
We also confirm that the addition is commutative:
\begin{align}
(\eta+\varepsilon)_{c} &= \eta_{c} + \varepsilon_{c}\\
    &= \varepsilon_{c} + \eta_{c}\\
    &= (\varepsilon + \eta)_{c}
\end{align}
This concludes that for each $F, G \in \HomAkmat,\, \mathrm{Hom}_{\HomAkmat}(F,G)$ is an Abelian group.
\end{subproof}
\begin{subproof}[Proof of (ii)]
Let $F, G, H \in \HomAkmat$ and let $\eta, \varepsilon \in \mathrm{Hom}_{\HomAkmat}(F,G)$,
$\varphi, \psi \in \mathrm{Hom}_{\HomAkmat}(G,H)$ and $x \in \Bbbk$.\\
The composition $\eta\varphi \in \mathrm{Hom}_{\HomAkmat}(F,H)$ is defined by component-wise matrix-multiplication,
i.e. $\forall c \in \mathcal{A}$
\begin{align*}
(\eta\varphi)_{c} := \eta_{c}\varphi_{c}
\end{align*}
and from this follows the bilinearity of the composition, since the matrix multiplication is bilinear.\\
This concludes the first part of the proof, i.e. $\HomAkmat$ is an Ab-category.
\end{subproof}

\item Next we show that $\HomAkmat$ is an additive category, i.e. it is
\begin{enumerate}
\renewcommand{\labelenumii}{(\roman{enumii})}
\item An Ab-category with
\item A dependent function $\oplus$ mapping a finite set $I$ and a collection $(F_{i})_{i\in I}$ of objects in $\HomAkmat$
to a corresponding direct sum $( \oplus_{i\in I} F_{i}, (\pi_{i})_{i\in I}, (\iota_{i})_{i\in I}, u_{\mathrm{in}}, u_{\mathrm{out}} )$.
\end{enumerate}
\begin{subproof}[Proof of (ii)]
Let $I = \{1,\dots,n\}$ be a finite set, and $F_{i} \in \HomAkmat, 1\leq i\leq n$. The object $F := \oplus_{i=1}^{n} F_{i}$ is a functor, mapping
each object $c \in \mathcal{A}_{0}$ to the natural number $Fc = \oplus_{i=1}^{n} F_{i}c := \sum_{i=1}^{n} F_{i}c \in \kmat_{0}$.\\
A morphism $a : c \rightarrow c' \in \mathcal{A}_{1}$ with $F_{i} a : F_{i} c \rightarrow F_{i} c', \, 1\leq i\leq n$ gets mapped to the matrix 
$F a : Fc \rightarrow Fc'$ that is the block-diagonal matrix of the $F_{i}a$'s.
In other words, we can identify each $F_{j}a$ as a $F_{j} c \times F_{j} c'$ submatrix:
\[
\left(F_{j}a\right)_{k,l} = \left(F a\right)_{\sum_{i=1}^{j-1} F_{i}c + k,\,\sum_{i=1}^{j-1} F_{i}c' + l},
1 \leq k \leq F_{j}c, 1 \leq l \leq F_{j}c'
\]

define $\pi_{i}, \iota_{i}$, for $\tau, \rho, u_{\mathrm{in}}(\tau), u_{\mathrm{out}}(\rho)$,

prove:
properties are fulfilled.

The sets of projections $\pi = \{ \pi_{i} : F \rightarrow F_{i} \}_{i = 1,\dots,n}$ and coprojections
$\iota = \{ \iota_{i} : F_{i} \rightarrow F \}_{i = 1,\dots,n}$ are sets of natural transformations,
where each $\pi_{i}$ and $\iota_{i}$ is defined by its components:\\
For $c \in \mathcal{A}_{0}$ we have $(\pi_{i})_{c} : Fc \rightarrow F_{i}c$ and $(\iota_{i})_{c} : F_{i}c \rightarrow Fc$ with\\
\begin{minipage}{.35\textwidth}
\[
\sum_{i=1}^{n} (\pi_{i})_{c} (\iota_{i})_{c} = 1_{Fc}
\]
\end{minipage}
\begin{minipage}{.1\textwidth}
and
\end{minipage}
\begin{minipage}{.55\textwidth}
\[
(\iota_{i})_{c}(\pi_{j})_{c} = (\delta_{i,j})_{c} = \begin{cases}
1_{F_{i}c} & \text{ if } i = j \\
0_{F_{i}c, F_{j}c} & \text{ if } i \neq j
\end{cases}
\]
\end{minipage}

For a family of natural transformations $\tau = \{ \tau_{i} : G \rightarrow F_{i} \}_{i = 1,\dots,n}$

\begin{align*}
\forall c \in \mathcal{A}_{0},&& &&  (\oplus_{i \in I} F_{i}) c &= \oplus_{i \in I} (F_{i} c) \\
\forall c \in \mathcal{A}_{0},&& \forall i \in I,&& (\pi_{i} : F \rightarrow F_{i})_{c} &= (\pi_{i})_{c} : Fc \rightarrow F_{i} c \\
\forall c \in \mathcal{A}_{0},&& \forall i \in I,&& (\iota_{i} : F_{i} \rightarrow F)_{c} &= (\iota_{i})_{c} : F_{i} c \rightarrow Fc \\
\forall c \in \mathcal{A}_{0},&& \forall \tau = \{ \tau_{i} : G \rightarrow F_{i} \}_{i = 1,\dots,n},&&
(u_{\mathrm{in}}(\tau))_{c} &= u_{\mathrm{in}}(\tau_{c}) \\
\forall c \in \mathcal{A}_{0},&& \forall \rho = \{ \rho_{i} : F_{i} \rightarrow H \}_{i = 1,\dots,n},&&
(u_{\mathrm{out}}(\rho))_{c} &= u_{\mathrm{out}}(\rho_{c})
\end{align*}

where $\tau_{c} = \{ (\tau_{i})_{c} : Gc \rightarrow F_{i} c \}_{i \in I}$ and $\rho_{c} = \{ (\rho_{i})_{c} : F_{i} c \rightarrow Hc \}_{i \in I}$.

\begin{align*}
u_{\mathrm{in}}(\tau_{c}) p_{i} &= (\tau_{i})_{c} \\
j_{i} u_{\mathrm{out}}(\rho_{c}) &= (\rho_{i})_{c}
\end{align*}

with $\{ p_{i} : Fc \rightarrow F_{i}c \}_{i\in I}$ and $\{ j_{i} : F_{i}c \rightarrow Fc \}_{i \in I}$ the projection and injection morphisms
of the direct sum of matrices.

Prove that $p_{i} = (\pi_{i})_{c}$ and $j_{i} = (\iota_{i})_{c}$.

The direct sum of a family of functors $\{ F_{i}\}_{i \in I}$ is a functor $F := \oplus_{i \in I} F_{i}$, mapping each object $c \in \mathcal{A}_{0}$
to an object $Fc \in \kmat_{0}$, where $Fc$ is the direct sum of the family $\{ F_{i}c \}_{i \in I}$.
The family of projections $\{ \pi_{i} : F \rightarrow F_{i} \}$ of the direct sum $F$ of functors is a family of natural transformations.
The components of the $\pi_{i}$ under the same object $c \in \mathcal{A}_{0}$ form a family of projections $\{ (\pi_{i})c : Fc \rightarrow F_{i} c\}$
that are the projections in factors of the direct sum $Fc$. Likewise for the family of injections.

We conclude that the 
\end{subproof}

\begin{subproof}[Proof of (ii)]
Let $I = \{1,\dots,n\}$ be a finite set. For each $c \in \mathcal{A}_{0}$ the family $(F_{i})_{i\in I}$ of functors in $\HomAkmat_{0}$ gets mapped to a
family $(S_{i})_{i\in I} := (F_{i}c)_{i\in I}$ of objects in $\kmat_{0}$. Let $S := \oplus_{i\in I} S_{i}$ be the direct sum of the $S_{i}$'s with projections
$p = \{ p_{i} : S \rightarrow S_{i}\}_{i\in I}$ and coprojections $j = \{ j_{i} : S_{i} \rightarrow S\}_{i\in I}$ as well as dependent functions
$v_{\text{in}}$ and $v_{\text{out}}$ such that each family of morphisms $t = \{ t_{i} : T \rightarrow S_{i}\}_{i\in I}$ gets mapped to a
morphism $v_{\text{in}}(t)$ and each family of morphisms $r = \{ r_{i} : S_{i} \rightarrow R\}_{i\in I}$ gets mapped to a
morphism $v_{\text{out}}(r)$ such that
\begin{align*}
v_{\text{in}}(t) p_{i} &= t_{i} \forall i\in I, \\
j_{i} v_{\text{out}}(r) &= r_{i} \forall i\in I.
\end{align*}
The $p$ and $j$ also satisfy
\begin{align*}
\sum_{i\in I} p_{i} j_{i} &= 1_{S} \text{  and  } \\
j_{i} p_{k} &= \begin{cases}
            1_{S_{i}} & \text{ if } i = k \\
            0_{ik} & \text{ if } i \neq k
        \end{cases}
\end{align*}
We now want to define a direct sum in the functor category, i.e. for the family $(F_{i})_{i\in I}$ the tuple
$(F = \oplus_{i\in I} F_{i}, \pi = (\pi_{i})_{i\in I}, \iota = (\iota_{i})_{i\in I}, u_{\text{in}}, u_{\text{out}})$ with the desired properties of a direct sum.
Let $F$ be the functor mapping each $c\in \mathcal{A}_{0}$ to the object $Fc := S = \oplus_{i\in I} F_{i}c$. This already fixes the source and target of
$Fa$ for a morphism $a : c \rightarrow c' \in \mathcal{A}_{1}$, namely
\begin{align*}
Fa &: Fc \rightarrow Fc' \\
Fa &: \oplus_{i\in I} F_{i}c \rightarrow \oplus_{i\in I} F_{i}c'
\end{align*}
$\pi$ such that $(\pi_{i})_{c} : Fc \rightarrow F_{i}c = p_{i} : S \rightarrow S_{i}$.
\end{subproof}

\item
\end{enumerate}
\end{proof}




